Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-11-20 paper/main_RA-L_v1_final.tex
Updated Video link in paper

\begin{figure*}[!ht]
  \begin{minipage}[b]{0.31\textwidth}
	\centering	
		\begin{subfigure}[t]{\linewidth}
		\centering
			\includegraphics[width=0.5\linewidth]{new-pics/forehand_crop.png}\hspace{5pt}\includegraphics[width=0.43\linewidth]{new-pics/backhand_crop.png}
					\caption{Forward/Backward Reaching (1-2).\label{fig:forback}}
		\end{subfigure}
		\begin{subfigure}[t]{\linewidth}
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-free_crop.png}\hspace{5pt}\includegraphics[width=0.477\linewidth]{new-pics/pour-obst_crop.png}
						\caption{ Pouring Motions (3-4)}
			\end{subfigure}
			\begin{subfigure}[t]{\linewidth}		
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-obst-2_crop.png}\hspace{5pt}\includegraphics[width=0.5\linewidth]{new-pics/footstep.png}
	\caption{ Pouring Motion (5) and Foot-step (6).}
				\end{subfigure}
    \captionof{figure}{Demonstrated Joint-Space Behaviors with Task-Space Targets. \href{https://www.dropbox.com/sh/3vx512oldgbnkq5/AABP5iEqO0oYn7dlE-gvK1kPa?dl=0}{[videos]} \label{fig:behaviors}}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.69\textwidth}
    \scriptsize
    \centering
\resizebox{\linewidth}{!}{\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

\begin{figure*}[t]
	\vspace{-0.05cm}
	\begin{subfigure}[t]{0.42\linewidth}
		\includegraphics[width=0.45\linewidth]{Pic/Luggage1.png}
		\includegraphics[width=0.143\linewidth]{Pic/Luggage2.png}
		\includegraphics[width=0.377\linewidth]{Pic/Luggage3.png}
		\caption{Execution of Pour Obstacle 2 learned through JT-DS.}
		\label{fig:snapshot:a}
	\end{subfigure}
	\begin{subfigure}[t]{0.567\linewidth}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage4_SEDS.png}\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}
		\caption{Execution of Pour Obstacle 2 learned through SEDS.}
		\label{fig:snapshot:b}
	\end{subfigure}\\	
	\caption{Snapshots of the robot experiments. A corresponding video is available on-line \href{https://youtu.be/1dgKfmN1UgE}{[video link]}.}
	\label{fig:snapshot}
	\vspace{-10pt}
\end{figure*}

>>>>

\begin{figure*}[!ht]
  \begin{minipage}[b]{0.31\textwidth}
	\centering	
		\begin{subfigure}[t]{\linewidth}
		\centering
			\includegraphics[width=0.5\linewidth]{new-pics/forehand_crop.png}\hspace{5pt}\includegraphics[width=0.43\linewidth]{new-pics/backhand_crop.png}
					\caption{Forward/Backward Reaching (1-2).\label{fig:forback}}
		\end{subfigure}
		\begin{subfigure}[t]{\linewidth}
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-free_crop.png}\hspace{5pt}\includegraphics[width=0.477\linewidth]{new-pics/pour-obst_crop.png}
						\caption{ Pouring Motions (3-4)}
			\end{subfigure}
			\begin{subfigure}[t]{\linewidth}		
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-obst-2_crop.png}\hspace{5pt}\includegraphics[width=0.5\linewidth]{new-pics/footstep.png}
	\caption{ Pouring Motion (5) and Foot-step (6).}
				\end{subfigure}
    \captionof{figure}{Demonstrated Joint-Space Behaviors with Task-Space Targets. \label{fig:behaviors}}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.69\textwidth}
    \scriptsize
    \centering
\resizebox{\linewidth}{!}{\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

\begin{figure*}[t]
	\vspace{-0.05cm}
	\begin{subfigure}[t]{0.42\linewidth}
		\includegraphics[width=0.45\linewidth]{Pic/Luggage1.png}
		\includegraphics[width=0.143\linewidth]{Pic/Luggage2.png}
		\includegraphics[width=0.377\linewidth]{Pic/Luggage3.png}
		\caption{Execution of Pour Obstacle 2 learned through JT-DS.}
		\label{fig:snapshot:a}
	\end{subfigure}
	\begin{subfigure}[t]{0.567\linewidth}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage4_SEDS.png}\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}
		\caption{Execution of Pour Obstacle 2 learned through SEDS.}
		\label{fig:snapshot:b}
	\end{subfigure}\\	
	\caption{Snapshots of the robot experiments. A corresponding video is available on-line \href{https://youtu.be/rirQkK0SSso}{[video link]}.}
	\label{fig:snapshot}
	\vspace{-10pt}
\end{figure*}
